Relating games of Menger, countable fan tightness, and selective separability

### 2017-08-26 articles/relating-games-menger-cft-ss/article.tex
help out arxiv
proofread menger paper

\usepackage{../../clontzDefinitions}

@@

\begin{definition}
  Let \(\mc B_{X,x}\) be the collection of subsets \(A\subset X\) where
  \(x\in\closure{A}\). (Call \(A\) a \term{blade} of \(x\).)
  Then \(\schSelProp{\mc B_{X,x}}{\mc B_{X,x}}\) is the
  \term{countable fan tightness property} for \(X\) at \(x\)
  (\(CFT_x\) for short), and
  \(\schSelGame{\mc B_{X,x}}{\mc B_{X,x}}\) is the
  \term{countable fan tightness game} for \(X\) at \(x\).
\end{definition}

@@

\begin{definition}
  Let \(\mc D_{X}\) be the collection of dense subsets of a topological
  space \(X\). (So, \(\mc D_X\subseteq \mc B_{X,x}\) for all \(x\in X\).)
  Then \(\schSelProp{\mc D_X}{\mc B_{X,x}}\) is the
  \term{countable dense fan tightness property} for \(X\) at \(x\)
  (\(CDFT_x\) for short), and
  \(\schSelGame{\mc D_X}{\mc B_{X,x}}\) is the
  \term{countable dense fan tightness game} for \(X\) at \(x\).
\end{definition}

@@

Note that \(CFT\Rightarrow CDFT\) for any space \(X\) as
\(\mc D_X\subseteq \mc B_{X,x}\).

@@

Of course, one may easily observe that a selective separable space is
separable. In \cite{MR2678950} Barman and Dow demonstrated that all
separable Frechet spaces are selectively separable. They were also able
to produce a space which is selectively separable, but does not allow
\(\plII\) a winning strategy in the selective separability game.

@@

The solution is already known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerGamePreprint} the author showed that while \(M^+\) implies
\(M^{+mark}\) for second-countable spaces, there exists a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{+mark}\).

@@

\begin{proof}
  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of open covers.
  For \(\Omega M\), choose the witness
  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) for the final
  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\) for each \(n<\omega\),
  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\).
  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
  \). For \(\Omega M^{+mark}\), the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(\mc U,n)
      =
    \bigcup_{i\leq n}\sigma(\mc U,i)
  \).
\end{proof}

@@

\begin{proof}
  For each \(B\in\mc B_{C_p(X),\vec 0}\) define
  \[
    \mc U_n(B)
      =
    \left\{
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
    :
      \vec x\in B
    \right\}
  .\]
  Consider the finite set \(F\in[X]^{<\omega}\). Since
  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
  It follows that \(F\subseteq x^{\leftarrow}[(-1,1)]\in\mc U_n(B)\),
  so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).

  Consider the sequence of blades
  \(\<B_0,B_1,\dots\>\in\mc B_{C_p(X),\vec 0}^\omega\), and the
  corresponding sequence of \(\omega\)-covers
  \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    F_n
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

@@

\begin{proof}
  For each \(\mc U\in\Omega_{X}\) define
  \[
    D(\mc U)
      =
    \{
      \vec y\in C_p(X)
    :
      \vec y[X\setminus U_{\vec y,\mc U}]=\{1\}
      \text{ for some }
      U_{\vec y,\mc U}\in\mc U
    \}
  .\]
  Consider the point \(\vec x\in C_p(X)\) and its basic open neighborhood
  \([\vec x,G,\epsilon]\). If \(\mc U\) is an \(\omega\)-cover
  of \(X\), \(G\subseteq U\) for some \(U_{\vec y,\mc U}\in\mc U\).
  Since \(X\) is
  \(T_{3\frac{1}{2}}\), \(X\setminus U_{\vec y,\mc U}\) is closed, and \(G\)
  is finite and disjoint from \(X\setminus U_{\vec y,\mc U}\),
  we may choose some function \(\vec y\in C_p(X)\) where
  \(\vec y[X\setminus U_{\vec y,\mc U}]=\{1\}\) and \(\vec x(t)=\vec y(t)\)
  for each \(t\in G\).
  It follows \(\vec y\in [\vec x,G,\epsilon]\cap D\), so \(D(\mc U)\)
  is dense in \(C_p(X)\).

@@

\begin{proof}
  Since \(\mc D_X\subseteq \mc B_{X,x}\), the second condition trivially
  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
  follow from \(C(D)FT_{\vec 0}\). So the result follows from the
  previous lemmas.
\end{proof}

@@

\begin{proof}
  Let \(X\) and therefore \(X^n\) be compact.
  Let \(\mc F_n\) be the finite subcover of the
  open cover \(\mc U_n=\{U^n:U\in\mc U\}\). Then
  \(\mc F=\{U:U^n\in\mc F_n\}\) witnesses our desired result.
\end{proof}

@@

\begin{proof}
  The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
  was shown in \cite{clontzMengerGamePreprint}. As \(\Omega M^{+mark}\)
  trivially implies \(M^{+mark}\), we need only demonstrate that
  if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
  then \(X\) is \(\Omega M^{+mark}\).

@@

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
  is simply the fact that its countably infinite subsets
  are closed and discrete.
  We define the strategy \(\sigma\) for \(\plII\) in
  \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.

  For \(n<\omega\)
  let \(\sigma(\<\mc U_0,\dots,\mc U_n\>)=\{U(\<\mc U_0,\dots,\mc U_n\>)\}\),
  where
  \[
    U(\<\mc U_0,\dots,\mc U_n\>)
      =
    \onePtLind{\omega_1}
      \setminus
    \{\alpha_{n,m}:m<\omega\}
  \]
  is a co-countable set
  containing \(\{\infty\}\cup\{\alpha_{i,j}:i,j<n\}\).

@@

@@

\begin{proof}
  Every metrizable topological space has points \(G_\delta\).
  However, if every neighborhood of \(\infty\) is
  co-countable, \(\{\infty\}\) cannot be the intersection of countably many
  open sets.
\end{proof}

@@

\section{Equivalence of certain strategic and Markov seleciton properties}

@@

  Since \(\<Z_{f\rest1},Z_{f\rest2},\dots\>\in\mc A^\omega\), it follows
  that
  \(
    \bigcup_{n<\omega}\sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n}\>)
      \in
    \mc B
  \).
  The result then follows from
  \begin{align*}
    \bigcup_{n<\omega}\tau(A_n,n)
      & =
    \bigcup_{n<\omega}
    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
      \\ & \supseteq
    \bigcup_{n<\omega,b(n)<f}
    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
      \\ & =
    \bigcup_{n<\omega,b(n)<f}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},A_{b^{\leftarrow}(f\rest|b(n)|)}\>)
      \\ & =
    \bigcup_{n<\omega,b(n)<f}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},Z_{f\rest(|b(n)|+1)}\>)
      \\ & =
    \bigcup_{n<\omega}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest n}\>)
      \\ & \in
    \mc B
  \end{align*}
  as \(\mc B\) is closed under supersets.
\end{proof}

@@

\begin{proof}
  First note that any witness for
  \(\Omega M^+\) is a witness for
  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\).
  Fix a countable base \(\mc B\) for \(X\) closed under finite unions, and let
  \(\Omega_X^*\) be the collection of \(\omega\)-covers of \(X\) which only
  use basic open sets. Then
  \(\bigcup\Omega_X^*=\mc B\) is countable, and any set containing an
  \(\omega\)-cover is an \(\omega\)-cover; therefore
  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\) if and only if
  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).

@@

\begin{corollary}[\cite{clontzMengerGamePreprint}]
  A second-countable space is \(M^+\) if and only if
  it is \(M^{+mark}\).
\end{corollary}

@@

  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^+\)
  for each \(i<\omega\). Define \(p:\omega\to\omega\) partition \(\omega\)
  into infinite sets \(\{p(i):i<\omega\}\).
  For a nonempty finite sequence \(t\), let \(t'\) be its subsequence removing
  all terms of index \(n\) such that \(p(n)\not=p(|t|-1)\).
  (Note that this process preserves the final term.)
  We then define the strategy \(\tau\) by
  \[
    \tau(t)
      =
    \sigma_{p(|t|-1)}(t')
  .\]

  Let \(\alpha\in\mc D_X^\omega\), and let \(\alpha_i\) be its subsequence
  removing all terms of index \(n\) such that \(p(n)\not=i\).
  By \(sCDFT_{d_i}^+\), we have
  \[
    d_i
      \in
    \cl{\{\sigma_i(\alpha_i\rest (n+1)):n<\omega\}}
      =
    \cl{\{\tau(\alpha\rest(n+1)):n\in p^{\leftarrow}(i)\}}
      \subseteq
    \cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}
  \]
  and as \(D\subseteq\cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}\)
  it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}}
      =
    \cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}
  .\]
  Therefore \(\tau\) witnesses \(SS^+\).

>>>>

\usepackage{clontzDefinitions}

@@

\begin{definition}
  Let \(\Omega_{X,x}\) be the collection of subsets \(A\subset X\) where
  \(x\in\closure{A}\). (Call \(A\) a \term{blade} of \(x\).)
  Then \(\schSelProp{\Omega_{X,x}}{\Omega_{X,x}}\) is the
  \term{countable fan tightness property} for \(X\) at \(x\)
  (\(CFT_x\) for short), and
  \(\schSelGame{\Omega_{X,x}}{\Omega_{X,x}}\) is the
  \term{countable fan tightness game} for \(X\) at \(x\).
\end{definition}

The similar notations for \(\omega\)-covers \(\Omega_X\) and
blades \(\Omega_{X,x}\) is well-established, see e.g.
\cite[Topological games and Ramsey theory]{19362020070101} (wherein
the notation is more succently given as \(\Omega,\Omega_x\)).  The
relationship between such sets becomes apparent in the study of
\(C_p\)-theory; for this reason we choose to always denote the space
explicitly to help distinguish the ambient spaces when discussing
the relationship between \(\Omega_X\) and
\(\Omega_{C_p(X),\vec 0}\).

@@

\begin{definition}
  Let \(\mc D_{X}\) be the collection of dense subsets of a topological
  space \(X\).
  Then \(\schSelProp{\mc D_X}{\Omega_{X,x}}\) is the
  \term{countable dense fan tightness property} for \(X\) at \(x\)
  (\(CDFT_x\) for short), and
  \(\schSelGame{\mc D_X}{\Omega_{X,x}}\) is the
  \term{countable dense fan tightness game} for \(X\) at \(x\).
\end{definition}

@@

Note that \(CFT\Rightarrow CDFT\) for any space \(X\) as
\(\mc D_X\subseteq \Omega_{X,x}\) for all \(x\in X\).

@@

Of course, one may easily observe that a selective separable space is
separable, and \(SS\Rightarrow CDFT\).
In \cite{MR2678950} Barman and Dow demonstrated that all
separable Frechet spaces are selectively separable. They were also able
to produce a space which is selectively separable, but does not allow
\(\plII\) a winning strategy in the selective separability game.

@@

The solution is already known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerCMUC} the author showed that \(M^+\) implies
\(M^{+mark}\) for second-countable spaces; however, the one-point
Lindel\"of-ication \(\onePtLind{\omega_1}\) of a discrete space of size
\(\omega_1\) is a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{+mark}\) (equivalently, not \(\sigma\)-compact).
It will later be shown that it is no coincidence
that countable \(SS^+\) implies \(SS^{+mark}\) and
second-countable \(M^+\) implies \(M^{+mark}\).

@@

\begin{proof}
  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of \(\omega\)-covers.
  For each \(n<\omega\), let
  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) witness \(\Omega M\) for the final
  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\),
  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\); it follows that
  \(\<\mc F_0,\mc F_1,\dots\>\) satisfies the proposition.

  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
  \). For \(\Omega M^{+mark}\), the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(\mc U,n)
      =
    \bigcup_{i\leq n}\sigma(\mc U,i)
  \). Both improved strategies are easily seen to satisfy the proposition.
\end{proof}

@@

\begin{proof}
  For each \(B\in\Omega_{C_p(X),\vec 0}\) define
  \[
    \mc U_n(B)
      =
    \left\{
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
    :
      \vec x\in B
    \right\}
  .\]
  Consider the finite set \(F\in[X]^{<\omega}\). Since
  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1/2^n]\).
  It follows that
  \(F\subseteq \vec x^{\leftarrow}[(-1/2^n,1/2^n)]\in\mc U_n(B)\),
  so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).

  Consider the sequence of blades
  \(\<B_0,B_1,\dots\>\in\Omega_{C_p(X),\vec 0}^\omega\), and the
  corresponding sequence of \(\omega\)-covers
  \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    F_n
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since \(\bigcup_{i\leq n<\omega} \mc F_n\)
  is an \(\omega\)-cover, we may choose
  \(i\leq n<\omega\) and
  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore, \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  is an \(\omega\)-cover, we may choose
  \(i\leq n<\omega\) and \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]
  \in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\),
  and thus every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\). Since
  \(\bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)\) is an \(\omega\)-cover,
  we may choose \(i\leq n<\omega\) and
  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

@@

\begin{proof}
  For each \(\mc U\in\Omega_{X}\) define
  \[
    D(\mc U)
      =
    \{
      \vec y\in C_p(X)
    :
      \vec y[X\setminus U_{\vec y,\mc U}]=\{1\}
      \text{ for some }
      U_{\vec y,\mc U}\in\mc U
    \}
  .\]
  Consider the point \(\vec x\in C_p(X)\) and its basic open neighborhood
  \([\vec x,G,\epsilon]\). If \(\mc U\) is an \(\omega\)-cover
  of \(X\), \(G\subseteq U\)
  for some \(U\in\mc U\).
  Since \(X\) is
  \(T_{3\frac{1}{2}}\), \(X\setminus U\) is closed, and \(G\)
  is finite and disjoint from \(X\setminus U\),
  we may choose some function \(\vec y\in C_p(X)\) where
  \(\vec y[X\setminus U]=\{1\}\) and \(\vec x(t)=\vec y(t)\)
  for each \(t\in G\).
  It follows \(\vec y\in [\vec x,G,\epsilon]\cap D(\mc U)\), so \(D(\mc U)\)
  is dense in \(C_p(X)\).

@@

\begin{proof}
  Since \(\mc D_X\subseteq \Omega_{X,x}\), the second condition trivially
  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
  follow from \(C(D)FT_{\vec 0}\). So the result follows from the
  previous lemmas.
\end{proof}

@@

\begin{proof}
  Let \(X\) and therefore \(X^n\) be compact.
  Let \(\mc F_n\) be the finite subcover of the
  open cover \(\mc U_n=\{U^n:U\in\mc U\}\). Then
  \(\mc F=\{U:U^n\in\mc F_n\}\) satisfies that for each \(F\in[X]^{\leq n}\)
  there exists some \(U\in\mc F\) where \(F\subseteq U\).

  Conversely, assume that for each \(\omega\)-cover
  \(\mc U\) of \(X\) and \(n<\omega\), there exists a finite subcollection
  \(\mc F\in[\mc U]^{<\omega}\) such that for each \(F\in[X]^{\leq n}\)
  there exists some \(U\in\mc F\) where \(F\subseteq U\). Given an
  arbitrary open cover \(\mc V\), close it under finite unions to obtain
  an \(\omega\)-cover \(\mc U\). Then the finite subcollection \(\mc F\)
  of \(\mc U\) is of course a finite subcover,
  and since each member of \(\mc F\) is a finite union of open sets in
  \(\mc V\), there exists a finite subcover \(\mc G\) of \(\mc V\).
\end{proof}

@@

\begin{proof}
  The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
  was shown in \cite{clontzMengerCMUC}. As \(\Omega M^{+mark}\)
  trivially implies \(M^{+mark}\), we need only demonstrate that
  if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
  then \(X\) is \(\Omega M^{+mark}\).

@@

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
  follows from the fact that its countably infinite subsets
  are closed and discrete, so all of its compact subsets are finite.

  To show \(\Omega M^+\),
  we define the strategy \(\sigma\) for \(\plII\) in
  \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.
  For a given partial play \(\<\mc U_0,\dots,\mc U_n\>\), suppose
  \(\{\alpha_{i,m}:i<n,m<\omega\}\subseteq\omega_1\) has already been defined.
  Then as \(\mc U_n\) is an \(\omega\)-cover, we may
  choose \(U(\<\mc U_0,\dots,\mc U_n\>)\in\mc U_n\) that contains
  \(\{\infty\}\cup\{\alpha_{i,j}:i,j<n\}\). Since
  \(U(\<\mc U_0,\dots,\mc U_n\>)\) is co-countable, define
  \(\{\alpha_{n,m}:m<\omega\}\) such that
  \(
    U(\<\mc U_0,\dots,\mc U_n\>)
      =
    \onePtLind{\omega_1}
      \setminus
    \{\alpha_{n,m}:m<\omega\}
  \). Then let
  \(\sigma(\<\mc U_0,\dots,\mc U_n\>)=\{U(\<\mc U_0,\dots,\mc U_n\>)\}\).

@@

Note that the preceding result could be worded more strongly:
\(\onePtLind{\omega_1}\)
is strategically \(\Omega\)-Rothberger, since the winning strategy only
uses a single set of the \(\omega\)-cover during each round.
This topic will be discussed further in a later section.

@@

\begin{proof}
  Consider a topology coarser than the topology of \(\onePtLind{\omega_1}\).
  Since open neighborhoods of \(\infty\) in this topology are co-countable,
  a countable intersection of \(\infty\) neighborhoods is not
  \(\{\infty\}\). Since every metrizable topological space has points
  \(G_\delta\), this topology cannot be metrizable.
\end{proof}

@@

\section{Equivalence of certain strategic and Markov selection properties}

@@

  Since \(\<Z_{f\rest1},Z_{f\rest2},\dots\>\in\mc A^\omega\), it follows
  that
  \(
    \bigcup_{n<\omega}\sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n}\>)
      \in
    \mc B
  \).
  Let \(b(n)\prec f\) denote that \(b(n)\in\omega^{<\omega}\) is a finite
  restriction of \(f\in\omega^\omega\).
  The result then follows from
  \begin{align*}
    \bigcup_{n<\omega}\tau(A_n,n)
      & =
    \bigcup_{n<\omega}
    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
      \\ & \supseteq
    \bigcup_{n<\omega,b(n)\prec f}
    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
      \\ & =
    \bigcup_{n<\omega,b(n)\prec f}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},A_{b^{\leftarrow}(f\rest|b(n)|)}\>)
      \\ & =
    \bigcup_{n<\omega,b(n)\prec f}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},Z_{f\rest(|b(n)|+1)}\>)
      \\ & =
    \bigcup_{n<\omega}
    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest n}\>)
      \\ & \in
    \mc B
  \end{align*}
  as \(\mc B\) is closed under supersets.
\end{proof}

@@

\begin{proof}
  Fix a countable base \(\mc B\) for \(X\) closed under finite unions, and let
  \(\Omega_X^*\) be the collection of \(\omega\)-covers of \(X\) which only
  use basic open sets.
  One may quickly verify that
  \(\Omega M^+\) implies
  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\).

  Note now that
  \(\bigcup\Omega_X^*=\mc B\) is countable, and any set containing an
  \(\omega\)-cover is an \(\omega\)-cover; therefore
  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\) if and only if
  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).

@@

\begin{corollary}[\cite{clontzMengerCMUC}]
  A second-countable space is \(M^+\) if and only if
  it is \(M^{+mark}\).
\end{corollary}

@@

  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^+\)
  for each \(i<\omega\). Define \(p:\omega\to\omega\) partitioning \(\omega\)
  such that \(|p^\leftarrow(i)|=\omega\) for all \(i<\omega\).
  Essentially, we will partition each
  attack by \(\plI\) according to \(p\) into \(\omega\)-many subattacks, and
  defeat each subattack to produce a blade of \(d_n\).

  For a nonempty finite sequence \(t\), let \(t'\) be its subsequence deleting
  all terms of index \(n\) where \(p(n)\not=p(|t|-1)\).
  Note that the final term of \(t\) is the final term of \(t'\).
  Thus the function \(\tau\) defined by
  \[
    \tau(t)
      =
    \sigma_{p(|t|-1)}(t')
  \]
  is a legal strategy.

  Let \(\alpha\in\mc D_X^\omega\) be an attack by \(\plI\),
  and let \(\alpha_i\) be its subsequence
  deleting all terms of index \(n\) where \(p(n)\not=i\).
  By \(sCDFT_{d_i}^+\), we have
  \[
    d_i
      \in
    \cl{\{\sigma_i(\alpha_i\rest (n+1)):n<\omega\}}
      =
    \cl{\{\tau(\alpha\rest(n+1)):n\in p^{\leftarrow}(i)\}}
      \subseteq
    \cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}
  \]
  and as \(D\subseteq\cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}\)
  it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}}
      =
    \cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}
  .\]
  Therefore \(\tau\) witnesses \(SS^+\).
